\begin{thebibliography}{1}
%reference for chapter one-->>Introduction
	\bibitem{doe} J. Doe. \emph{Book on foobar.} Publisher X,
	2300.
	\bibitem{intro1} J. Doe. \emph{Book on foobar.} Publisher X,
	2300.

%reference for chapter two-->>Background
	\bibitem{ros}
		Quigley, Morgan., Conley, Ken., Gerkey, Brian P.., Faust, Josh., Foote, Tully., Leibs,
		``ROS: an open-source Robot Operating System'' in: Conference Paper; 2009. \url{http://www.willowgarage.com/papers/ros-open-source-robot-operating-system}	
	\bibitem{pcl}
		Radu Bogdan Rusu and Steve Cousins,
		``3D is here: Point Cloud Library (PCL)'' in: IEEE International Conference on Robotics and Automation (ICRA); 2011. \url{http://pointclouds.org/assets/pdf/pcl_icra2011.pdf}
	
	\bibitem{open3d}
	Qian-Yi Zhou and Jaesik Park and Vladlen Koltun,
	``{Open3D}: {A} Modern Library for {3D} Data Processing'' arXiv:1801.09847; 2018. \url{http://www.open3d.org/}

	\bibitem{icp}
		P. J. Besl and N. D. McKay,
		``A method for registration of 3-D shapes''in: PAMI:1801.09847;1992.
	\bibitem{normal}
		Klaas Klasing, Daniel Althoff, Dirk Wollherr and Martin Buss,
		``Comparison of  Surface Normal Estimation  Methods for Range Sensing Applications'' 
	\bibitem{fpfh}
		Radu Bogdan Rusu, Nico Blodow, Michael Beetz,
		``Fast Point Feature Histograms (FPFH) for 3D Registration'' in: IEEE International Conference on Robotics and Automation, Kobe International Conference Center Kobe, Japan, May 12-17, 2009.
		
	\bibitem{cloudcompare}
		CloudCompare,
		\url{https://www.danielgm.net/cc/}

	\bibitem{meshlab}
		P. Cignoni, M. Callieri, M. Corsini, M. Dellepiane, F. Ganovelli, G. Ranzuglia,
		"MeshLab: an Open-Source Mesh Processing Tool" in: Sixth Eurographics Italian Chapter Conference, page 129-136, 2008, \url{http://www.meshlab.net/}.

    	\bibitem{freecad}
		FreeCAD,
		\url{https://www.freecadweb.org/}
\end{thebibliography}
