\documentclass[10]{article}
%\usepackage{fullpage}
%\usepackage[top=1in,bottom=1in,left=1in,right=1in]{geometry}

\usepackage[margin=1in,paperwidth=8.5in,paperheight=11in]{geometry}



\begin{document}

\title{Algebra 1 G/T chapter 1, part 1}
\author{Sinchiguano Cesar}
\date{\today}
\maketitle



\section{Critical Thinking Questions(something)(20pts)}
We’re always looking for ways to get our kids to think more deeply. Critical thinking skills are really important. So, we’ve rounded up all of the best critical thinking questions to help you get your students to the next level. 

\begin{enumerate}

    \item Who caused harm?
    \item Who was the most important character?
    \item Who is responsible?
    \item Who should have won?
    \item Who would benefit?
    \item Who would be affected by this?

\end{enumerate}

\section{Critical Thinking Questions That Start With What}
Now that you’ve got a big, long list of critical thinking questions to ask your students, are you looking for more information on teaching critical thinking skills? Check out this article: 10 Tips for Teaching Kids to Be Awesome Critical Thinkers Plus, get advice from other teachers by joining our Facebook group: WeAreTeachers Helpline. 

\begin{enumerate}

    \item  What would it be like if … ?
    \item Who was the most important character?
    \item What could happen if … ?
    \item Who should have won?
    \item Who would benefit?
    \item What is that character’s motive? 

\end{enumerate}

\section{Critical Thinking Questions That Start With When}
Had I known that bathroom breaks would be few and far between, I would have started doing Kegel exercises in seventh grade. Bladder training 101 would be comprised of various activities to aid in the art of “holding it in.” Students in this course would master the skills of learning how to survive on minimal liquids throughout the day, the art of ignoring the pain, and pee dances guaranteed to distract you from that nagging feeling that you might wet your pants at any given moment.
\begin{enumerate}
    \item When did the story change?
\item    When is this (un)acceptable?
    \item When does this become a problem? 
    \item When will we be able to tell if it worked?
\item    When is it time to stop?
    
\end{enumerate}





 


\end{document}